CODE CHECK

### 2020-05-27 codecheck-paper.Rmd

- https://paperpile.com/shared/rVNwBS
- https://medium.com/bits-and-behavior/a-modern-vision-for-peer-review-d5f73f0fae07 - work by Amy J. Ko: https://faculty.washington.edu/ajko/publications
  - is CODE CHECK's process too small, too incremental a change?
- overview of peer review and bibliometrics (if not a reference itself, it gives plenty of references): http://juser.fz-juelich.de/record/865096/files/Peer%20Review%20and%20Bibliometrics.pdf
- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
  - https://medium.com/@NeurIPSConf/call-for-papers-689294418f43
  - https://www.journals.elsevier.com/information-systems/editorial-board/
  - SIGMOD Reproducibility Review?
  - Biostatistics "AER" (https://academic.oup.com/biostatistics/article/10/3/405/293660)
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...
- Artefact Evaluation - https://www.artifact-eval.org/about.html
- continuous analysis - https://www.nature.com/articles/nbt.3780
- "A Universal Identifier for Computational Results" > https://www.sciencedirect.com/science/article/pii/S1877050911001256
- Discussion about using Docker containers during JOSS reviews > https://github.com/openjournals/joss/issues/498#issuecomment-462046912
- https://scigen.report, an independent site for registering reproductions, via https://annakrystalli.me/talks/ro-reprohack.html#32
  - example https://scigen.report/reviews/get?doi=10.1063/1.1823034
  - seems to be closed infrastructure
- new journal _ReScienceX_ (about experiments) also seems to have an ECR angle, https://www.nature.com/articles/d41586-020-01328-2

>>>>

- https://paperpile.com/shared/rVNwBS
- Are "Replicated Computations Results (RCR) Report" a thing? apparently so (using ACM terminology)
  - https://dl.acm.org/doi/10.1145/3185337
  - http://users.iems.northwestern.edu/~nelsonb/Publications/Nelson_RCRgreenSim.pdf
  - https://dl.acm.org/doi/epdf/10.1145/3341094
    - citation for replicated workflow lists it as "to appear"
  - getting proper papers for reproductions != CODECHECK approach where we want credit as reviewers
- https://medium.com/bits-and-behavior/a-modern-vision-for-peer-review-d5f73f0fae07 - work by Amy J. Ko: https://faculty.washington.edu/ajko/publications
  - is CODE CHECK's process too small, too incremental a change?
- overview of peer review and bibliometrics (if not a reference itself, it gives plenty of references): http://juser.fz-juelich.de/record/865096/files/Peer%20Review%20and%20Bibliometrics.pdf
- _Successes and struggles with computational reproducibility: Lessons from the Fragile Families Challenge_ > https://osf.io/preprints/socarxiv/g3pdb/
- community standards for software, cf. slide 6 in https://figshare.com/articles/_/5675104
  - "good enough practice" is "get a colleague to try using it", slide 19 in https://figshare.com/articles/_/5675104
- journals doing code reviews
  - _"We know of 16 journals that take this valuable step (ie TOP Level 3): AEA as already mentioned, plus others in polisci, psychology, biostats, and org chem: see Data Rep Policies here https://t.co/plOF8j6ADU "_ (https://twitter.com/EvoMellor/status/1202692360456589339?s=09); see also whole thread!
  - https://medium.com/@NeurIPSConf/call-for-papers-689294418f43
  - https://www.journals.elsevier.com/information-systems/editorial-board/
  - SIGMOD Reproducibility Review?
  - Biostatistics "AER" (https://academic.oup.com/biostatistics/article/10/3/405/293660)
- open science platforms/cloud services > https://www.nature.com/articles/d41586-019-03366-x
- live code in articles > o2r, eLife RDS https://www.nature.com/articles/d41586-019-00724-7, ...
- Artefact Evaluation - https://www.artifact-eval.org/about.html
- continuous analysis - https://www.nature.com/articles/nbt.3780
- "A Universal Identifier for Computational Results" > https://www.sciencedirect.com/science/article/pii/S1877050911001256
- Discussion about using Docker containers during JOSS reviews > https://github.com/openjournals/joss/issues/498#issuecomment-462046912
- https://scigen.report, an independent site for registering reproductions, via https://annakrystalli.me/talks/ro-reprohack.html#32
  - example https://scigen.report/reviews/get?doi=10.1063/1.1823034
  - seems to be closed infrastructure
- new journal _ReScienceX_ (about experiments) also seems to have an ECR angle, https://www.nature.com/articles/d41586-020-01328-2
